Natural Stories

### 2020-04-30 Analysis/nat_stories.Rmd
minor changes

---
title: "Natural Stories"
output: github_document
---
```{r, include=F}
knitr::opts_chunk$set(echo = FALSE, warning=F)
options(knitr.table.format = "html")
library(tidyverse)
library(readr)
library(brms)
library(lme4)
library(rstan)
library(tidybayes)
library(knitr)
library(viridis)
theme_set(theme_bw())
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())
```

@@

There's lots of ways to try to get at participant diligence that we might want to use for exclusions. IN particular, it appears that mean accuracy is correlated with mean rt -- people with high accuracy take longer than people who look like they are randomly guessing. In this experiment, we have an additional source of insight into diligence -- comprehension question accuracy. In the SPR natural stories experiment, they used 5 out of 6 comprehension questions correct as their threshold for data inclusion.

@@

ggplot(for_plot, aes(x=pct_correct, y=mean_rt, color=accurate))+
  geom_point(size=1)+
  scale_color_viridis(discrete=T)+
  labs(x="Fraction words selected correctly",
       y="Mean reaction time",
       color="?s correct")+
  coord_cartesian(xlim=c(0.4,1), ylim=c(0,1600))+
    scale_color_manual(values=c(">80% correct"="darkgreen","<80% correct"="darkred"))+
  guides(color=FALSE)

ggsave("../Papers/error.pdf", width=3, height=2, unit="in")

@@

>>>>

---
title: "Natural Stories"
output: github_document
---
```{r, include=F}
knitr::opts_chunk$set(echo = FALSE, warning=F)
options(knitr.table.format = "html")
library(tidyverse)
library(readr)
library(brms)
library(lme4)
library(rstan)
library(tidybayes)
library(knitr)
library(viridis)
library(cowplot)
theme_set(theme_bw())
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())
```

@@

There's lots of ways to try to get at participant diligence that we might want to use for exclusions. In particular, it appears that mean accuracy is correlated with mean rt -- people with high accuracy take longer than people who look like they are randomly guessing. In this experiment, we have an additional source of insight into diligence -- comprehension question accuracy. In the SPR natural stories experiment, they used 5 out of 6 comprehension questions correct as their threshold for data inclusion.

@@

ggplot(for_plot, aes(x=pct_correct, y=mean_rt, color=accurate))+
  geom_point(size=1)+
  scale_color_viridis(discrete=T)+
  labs(x="Fraction words selected correctly",
       y="Mean Reaction Time (ms)",
       color="?s correct")+
  coord_cartesian(xlim=c(0.4,1), ylim=c(0,1600))+
    scale_color_manual(values=c(">80% correct"="darkgreen","<80% correct"="darkred"))+
  guides(color=FALSE)

ggsave("../Papers/error.pdf", width=3, height=2.1, unit="in")

@@

# Error analysis

```{r}

b <- data_filt %>% filter(correct=="no") %>%
  filter(type!="practice") %>%
  select(word_num, subject, sentence) %>%
  group_by(subject, sentence) %>%
  mutate(row_num=row_number()) %>%
  filter(row_num==1) %>%
  select(-row_num) %>%
  left_join(for_plot, by="subject")

c <- data_filt %>% filter(type!=practice) %>%
  group_by(subject, sentence) %>%
  mutate(is.error=ifelse(correct=="no",1,0)) %>%
  summarize(mistakes=sum(is.error)) %>%
  mutate(no_mistake=ifelse(mistakes==0,"Error-free","Errorful")) %>%
  select(subject, sentence, no_mistake) %>%
  left_join(for_plot, by="subject")

a <- ggplot(b, aes(x=word_num, fill=accurate))+geom_bar()+facet_grid(.~accurate)+scale_fill_manual(values=c(">80% correct"="darkgreen","<80% correct"="darkred"))+
  labs(title="Locations of first mistakes", x="Word position (0 is a fake choice), x-axis cut at 30")+coord_cartesian(xlim=c(0,30))+
  guides(fill=F)

d <- ggplot(c, aes(x=no_mistake, fill=accurate))+geom_bar()+facet_grid(.~accurate)+scale_fill_manual(values=c(">80% correct"="darkgreen","<80% correct"="darkred"))+
  labs(title="Number of sentences completed correctly", x=NULL)+
  guides(fill=F)

plot_grid(a,d,ncol=1, rel_heights=c(1,.75))

Even more evidence some participants are taking the random button pressing; also more evidence that some others are doing quite well.
